Using Scagnostics to find Interesting Projections of Multivariate Data

### 2018-02-15 scagnostics.Rmd
adding to intro

@@

A large number of projection pursuit indices have been developed [@f87] [@CBC92] [@Lee05] [@AHC02] [@CEM:CEM2568] [@JS87] [@5508437].

*** Motivating example

>>>>

- name: Heike Hofmann
  affiliation: Department of Statistics, Iowa State University

- name: Hadley Wickham
  affiliation: RStudio

- name: Antony Unwin
  affiliation: Department of Mathematics, Augsburg University

- name: Katrin Grimm
  affiliation: ???

@@

A large number of projection pursuit indices have been developed [@f87] [@CBC92] [@Lee05] [@AHC02] [@CEM:CEM2568] [@JS87] [@5508437]. Many of these are developed to detect departure from multivariate normal, which includes clusters or outliers, or nonlinearity. Some have been developed to detect separations between known groups. However, if one wants to find unusual shapes, or shape differences between groups there are no options. One reason, is that it is hard, because defining what is meant by shape is not straightforward. An approach that seems plausible begins with scagnostics, developed by @scag, and explored in @WW08.

*** Motivating example ??

Scagnostics are scatterplot diagnostics. They were primarily developed to extract pairs of interesting variables from a large collection. XXX (Ursula to fill in based loosely on material at the German language wikipedia page - it would be good to translate this page and provide an English version on wikipedia)
